{\tt APFELgrid}: a fast interface to hadronic observables for fits of parton densities

### 2016-04-20 paper.tex
editing the introduction

In this paper we present a public implementation of the {\tt
  FastKernel} method in which the partonic hard cross sections are
taken from any given {\tt APPLgrid} look-up table while the DGLAP
evolution kernels are provided by {\tt APFEL}
code~\cite{Bertone:2013vaa}. We named the resulting code {\tt
  APFELgrid}.

>>>>

In this paper we present a public implementation of the {\tt
  FastKernel} method in which the partonic hard cross sections are
taken from any given {\tt APPLgrid} look-up table while the DGLAP
evolution kernels are provided by the {\tt APFEL}
code~\cite{Bertone:2013vaa}. We named the resulting code {\tt
  APFELgrid}.
